Model LF

### 2022-11-02 max_dp endogen stød.Rmd
Commit

```{r}
plot(part_000, col= "red"); lines(part, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```

@@

plot(wage_gap_02, col= "red", xlab= "Year", ylab= "Wage Gap in percent of wage", main= "Wage Gap"); lines(wage_gap_bs2, col = "blue");
legend("top",legend=c("Scenario 1", "Scenario 2"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

@@

@@

>>>>

```{r}
plot(part_000, col= "red"); lines(part_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```
```{r}

plot(((lf_000 - lf_bs1)*1000), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

@@

**Ratios**

@@

**Level**

plot(((pconk_ds_02 - pconk_ds_bs2)), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_02 - ik_bs2)), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

plot(((net_balance_02 - net_balance_bs2)), col= "black", xlab= "Year", ylab= "change in net exports as percentage of BNP", main= "Net-export");
grid()

@@

```{r}
plot(((lf_07b - lf_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in labor force (people)", main= "Change in Labor force");
grid()
```
